On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-06-07 Manuscript/manuscript.tex
Faceted Interval Plots

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/pct}
  \caption{100 replicate Percentile Bootstrap CIs for samples of $n = 800$ for
    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$. }
  \label{fig:pct}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/bc}
  \caption{100 replicate Bias-Corrected Bootstrap CIs for samples of $n = 800$ for
    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
  \label{fig:bc}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/prop}
  \caption{100 replicate Proposed Method CIs for samples of $n = 800$ for
    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$.}
  \label{fig:prop}
\end{figure}

As shown in Figure~\ref{fig:phi}, Percentile CIs appear to suffer from bias;
specifically, they seem to heavily underestimate $\phi$. As shown in
Figure~\ref{fig:bc}, $BC$ CIs do seem to correct this bias on average, but the width of
  the 
CIs is very inconsistent. From Figure~\ref{fig:prop}, we can see that the 
Proposed Method CIs correct the bias using 
$\widehat{\text{bias}} = \bar\theta_n^{(b)} -
  \hat\theta_n$, which seems to usually be negative, indicating a positive 
	correction from interval construction in Section~\ref{sec:bbci}.

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
  \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method Bootstrap CIs for samples of $n = 800$ for
    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
    of the CIs are displayed, as well as $\hat\theta_n$ and $\bar\theta_n^{(b)}$. }
  \label{fig:npi}
\end{figure}

As shown in Figure~\ref{fig:npi}, Percentile CIs appear to suffer from bias;
specifically, they seem to heavily underestimate $\phi$. $BC$ CIs do seem to correct this bias on average, but the width of
  the 
CIs is very inconsistent. We can see that the 
Proposed Method CIs correct the bias using 
$\widehat{\text{bias}} = \bar\theta_n^{(b)} -
  \hat\theta_n$, which seems to usually be negative, indicating a positive 
	correction from interval construction in Section~\ref{sec:bbci}.
